Illuminating a Dark Lens : A Type Ia Supernova \\ Magnified by Galaxy Cluster Abell 2744

### 2015-04-05 snTomas.tex
added System 3.3 fig and Intro, updated authors.tex, updated mag fig and lensingtest fig

\begin{abstract}
SN \tomas\ is a Type Ia Supernova (\SNIa) discovered at
$z=1.31\pm0.01$ behind the galaxy cluster Abell 2744 ($z=0.308$). This
SN has a projected separation from the cluster core of
$\sim$40\arcsec, closer to the critical lensing line than any previous
cluster-lensed \SNIa.  As such, it provides a valuable opportunity to
confront gravitational lens models of galaxy clusters with the direct
measurement of an absolute magnification at the edge of the
strong-lensing region.  We derive a tightly constrained measure of the
peak apparent magnitude, corrected for light curve shape and
exinction.  In a cosmology-independent analysis, we find that \tomas\
is \change{$0.75\pm0.15$} magnitudes brighter than unlensed \SNeIa\ at
similar redshift, implying a lensing magnification
of \change{$\mu_{\rm obs}=2.00\pm0.28$}.  We compare this direct
measurement of the magnification against predicted magnifications
from \change{14 lens models,} representing a broad range of
methodologies and incorporating a variety of strong- and weak-lensing
constraints.  The models are collectively fairly accurate. \change{
Half of the models deliver median magnifications that are consistent
with the measured $\mu$ to within the 1$\sigma$ uncertainties.}
However, the models are systematically biased to higher values: none
of the tested models predict a magnification equal to or lower than
the observed $\mu$, and some models are more than $5\sigma$ above the
measured magnification.  We evaluate possible causes for this bias,
and find that intercomparison of the lens models rules out several
simple possibilities.  A larger sample of $\sim$10 \SNeIa\ behind any
single cluster could provide a robust evaluation of systematic biases
in lens models.  Until such a sample exists, it is advisable
to \change{increase the estimated uncertainty of predicted
magnifications to match the dispersion observed across multiple lens
models.}
\end{abstract}

@@

\textcolor{red}{TODO: write and polish introduction}.
Massive galaxy clusters can be used as cosmic telescopes to magnify
distant background objects through gravitational lensing.  This can
substantially increase the reach of deep imaging surveys, and has
recently been used to discover candidate proto-galaxies formed in the
first Gyr after the Big 
Bang \citep{Zheng:2012,Coe:2013} 
\textcolor{red}{(cite other high-z galaxy candidates discovered with lensing)}

\textcolor{red}{TODO: describe past examples of lensed SN studies  \citep{Goobar:2009,Riehm:2011,Li:2012,Quimby:2014}.}

\citet[][hereafter P14]{Patel:2014} and \citet{Nordin:2014} presented
independent analyses of three lensed SNe, of which at least 2 are securely
classified as Type Ia SNe.  All of these three objects were found in
the Cluster Lensing and Supernova survey with Hubble (CLASH,
PI:Postman, HST Program ID 12068).

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{FIG/snTomas_magnifications}
\caption{ 
Comparison of the observed lensing magnification to predictions from
lens models. Solid vertical lines show the constraints from SN \tomas\
derived in Section~\ref{sec:Magnification} using the SALT2 (red) and
MLCS2k2 (blue) fitters, with shaded regions marking the total
uncertainty for each. Markers with horizontal error bars show the
median magnification and 68\%\ confidence region from each of the 14
lensing models.  Circles indicate models that use only strong-lensing
constraints, while diamonds denote those that also incorporate
weak-lensing measurements.  Models shown with open markers were
constructed using only data available before the start of the Frontier
Fields observations.  Filled markers indicate models that use
additional input constraints, including new multiply imaged systems
and redshifts.  The seven models shown in black at the top are from
the ``parametric'' family, and the four in green at the bottom are
``free-form.''  The dashed grey line marks the unweighted mean of all
model magnifications.
\label{fig:lensingtest} }
\end{center}
\end{figure}

@@

In Figure~\ref{fig:lensingtest} the model predictions are plotted
alongside the observed magnification of SN \tomas, derived in
Section~\ref{sec:Magnification}.  This comparison shows that these 11
models are largely consistent with each other. Naively treating each
model as an independent prediction for the magnification (and ignoring
their quoted uncertainties), one would get a mean for the full sample
of $\mu=2.51\pm0.34$ (shown as a grey dashed line in
Figure~\ref{fig:lensingtest}).  This is separated from the observed SN
magnification by $\delta\mu/\mu=30\%$, which is a 1.7$\sigma$
difference.

The models shown in Figure~\ref{fig:lensingtest} are separated along
the $y$ direction into two broad classes, with the
six \change{so-called} {\it parametric}\footnote{\change{Although this
nomenclature is becoming standard in the literature, it is somewhat
misleading, as the pixels or grid cells in free-form models are
effectively parameters as well. Perhaps ``simply-parameterized'' would
be more accurate, though we adopt the more common usage here.}}
models on top and the four {\it free-form} models on the bottom.
Broadly speaking, the parametric models use parameterized density
distributions to describe the arrangement of mass within the cluster,
typically associating massive dark matter halos with the positions of
bright cluster member galaxies. Therefore, parametric models rely (to
varying degrees) on the assumption that the observed light from
cluster galaxies is a good tracer of the cluster's dark matter.
Free-form models divide the cluster into a grid, generally using a
\change{multi-scale grid} to get better sampling in denser regions. Each grid cell
is assigned a mass or a potential, and then the mass values are
iteratively refined to match the observed lensing
constraints. \change{In some cases an adaptive grid is used so
that the grid spacing itself can also be modified as the model is
iterated \citep[e.g.][]{Liesenborgs:2006,Merten:2009}.}

@@

Figure~\ref{fig:lensingtest} also separates the models based on the
scope of input data constraints used.  Seven of the models rely only
on strong-lensing constraints (plotted as circles), while the other
four also use weak-lensing measurements (diamonds).  Eight of the
models were constructed using only pre-HFF data (open symbols), and
three others added new multiply-imaged systems and redshifts.

@@

At the outset of the HFF survey, only 33 multiply-imaged galaxies
behind Abell 2744 were known.  One might expect that the addition of
new lensing constraints from the HFF data would improve the model
constraints and reduce the tension between the predicted and observed
magnification.  However, for both of the most recent
models \citep{Jauzac:2014c,Lam:2014} that include new strong-lensing
constraints, the predicted magnification is still significantly higher
than the observed value.  Again the CATS model family provides a
useful case study.  The Jauzac model shares the same lens modeling
software (LensTool), and the same primary methodology as the earlier
CATS models.  A key difference is that the Jauzac model incorporates
many new multiply imaged galaxies and corrects a mis-identified
multiply-imaged system near the SN \tomas\ position.  These
improvements should in principle make the Jauzac model magnification
estimates more accurate, though we in fact see the opposite result:
the Jauzac model predicts a $\mu$ that is higher than the measured
value by $5.6\sigma$.

This shift to higher magnifications is not, however, unique to the
SN \tomas\ position.  \citet{Jauzac:2014c} noted that their updated
mass model of Abell 2744 results in a systematic increase in the
magnification values across the cluster field. Examining a sample of
$\sim$30 multiple images, \citeauthor{Jauzac:2014c} found that the
magnifications increased by a factor of $\sim1.5$ relative to pre-HFF
models.  Although this single sight-line can only provide a very
limited test of the model, the $5.6\sigma$ discrepancy is at least a
strong suggestion that improving the number and quality of
strong-lensing constraints can still lead to magnification maps that
are susceptible to systematic biases.

\change{
\subsection{Misidentification of System 3}
\label{sec:MisidentificationOfSystem3}
}
\change{
It is important to note that in regards to the impact on this
particular sight-line, not all strong-lensing constraints are equal.
An error in the association of multiple images or in the redshift of a
multiply-imaged galaxy would have a more significant impact if that
system has a projected position close to our SN
sight-line \changeG{\citep[see][for a quantitative assessment of this
effect]{Johnson:2014}.}  It happens that there is one such system, for
which the position of a multiple image near SN \tomas\ is presently
disputed.  }

\change{
This multiply-imaged galaxy was originally labeled as {\it System 3}
in \citet{Merten:2011}.  As shown in Figure~\ref{fig:System3}, it is
stretched into two adjacent arcs northwest of the cluster core (images
3.1 and 3.2), with a third image on the western edge of the
strong-lensing region (image 3.3 at 00:14:18.595,
-30:23:58.42).  \citet{Richard:2014} echoed this initial
identification in producing the {\tt CATS} models, which we cite in
Table~\ref{tab:PredictedMagnifications} and
Figure~\ref{fig:lensingtest}.  In developing the {\tt Sharon-v2}
models, \citet{Johnson:2014} provided a secure spectroscopic
constraint of $z=3.98\pm0.02$ for this system, based on a spectrum of
the combined 3.1+3.2 source. The identification of the original image
3.3 has been called into question by two independent analyses.  Using
HFF imaging data, \citet{Lam:2014} suggested an alternative third
image for this system roughly 8\arcsec\ to the south, which we will
call \33p\ (00:14:18.39, -30:24:06.53).
However, \citeauthor{Lam:2014} rejected this possibility based on a
difference in colors between \33p\ and images 3.1 and 3.2.  In
contrast, \citeauthor{Jauzac:2014c} argue that the position \33p\
is correct, and find that reassigning this multiple image results in a
tighter model reconstruction for the locations of other
multiply-imaged systems in the vicinity.
}

@@

\change{
Is it possible that \tomas\ is an example of a peculiar stellar
explosion that does not follow the relationship between light curve
shape and luminosity observed in normal Type Ia SNe?  In
Sections~\ref{sec:SNID} and \ref{sec:PhotometricClassification} we
classified SN Tomas as a normal Type Ia SN based on both the
spectroscopic and photometric evidence.  This rules out the
possibility that \tomas\ belongs to a different class of normal SN
explosions (Type Ib, Ic, or II). In
Section \ref{sec:LightCurveFitting} we fit the \tomas\ light curve to
determine a luminosity distance and found that the light curve shape
and color are consistent with a Type Ia SN of average light curve
width, with minimal dust extinction.  This excludes the possibility
that \tomas\ is one of the sub-class of ``fast declining'' Type Ia SNe
like SN 1991bg.
}

@@

\changeG{
At least for this particular sight-line, the free-form models perform
better in the sense that they deliver more realistic uncertainties.
This may indicate that the free-form approach in general is more
successful in capturing the uncertainty from biases inherent to the
mass modeling exercise, such as the mass sheet degeneracy and more
complex ``approximate
invariances'' \citep{Liesenborgs:2012,Schneider:2014}.  }

@@

\change{
A promising avenue for exploring the origins of systematic biases in
cluster lens models is through the use of simulated data.  One can
start with very deep high-resolution multi-band imaging on an unlensed
field that has a fairly complete spectroscopic redshift catalog, such
as the Hubble Ultra Deep Field.  Then a simulated galaxy cluster is
placed in the field, and the background galaxies are distorted into
arcs and multiple images using a well-defined lensing prescription.
The artificially lensed images can then be distributed to lens
modeling teams who attempt to reconstruct the (known) mass profile of
the simulated cluster.  This exercise has recently been pursued with a
set of synthetic clusters similar to those observed in the HFF program
(Meneghetti et al. in prep).  Preliminary analysis of this simulation
comparison suggests that systematic biases such as we have seen for
SN \tomas\ may be common for sources that lie close to the critical
curve in elongated and highly asymmetric clusters like Abell 2744.
This SN analysis indicates that such simulation efforts will be an
important step for moving toward precision science with cluster-lensed
sources. 
}

>>>>

\begin{abstract}
SN \tomas\ is a Type Ia Supernova (\SNIa) discovered at
$z=1.31\pm0.01$ behind the galaxy cluster Abell 2744 ($z=0.308$). This
SN has a projected separation from the cluster core of
$\sim$40\arcsec, closer to the critical lensing line than any previous
cluster-lensed \SNIa.  As such, it provides a valuable opportunity to
confront gravitational lens models of galaxy clusters with the direct
measurement of an absolute magnification at the edge of the
strong-lensing region.  We derive a tightly constrained measure of the
peak apparent magnitude, corrected for light curve shape and
exinction.  In a cosmology-independent analysis, we find that \tomas\
is \change{$0.75\pm0.15$} magnitudes brighter than unlensed \SNeIa\ at
similar redshift, implying a lensing magnification
of \change{$\mu_{\rm obs}=2.00\pm0.28$}.  We compare this direct
measurement of the magnification against predicted magnifications
from \change{14 lens models,} representing a broad range of
methodologies and incorporating a variety of strong- and weak-lensing
constraints.  The models are collectively fairly accurate: \change{
half of the models deliver median magnifications that are consistent
with the measured $\mu$ to within the 1$\sigma$ uncertainties.}
However, the models are systematically biased to higher values: none
of the tested models predict a magnification equal to or lower than
the observed $\mu$, and three models are $2-4\sigma$ above the
measured magnification.  We evaluate possible causes for this bias,
\changeG{considering both modeling errors and misinterpretation of the SN
data. Although we find no single explanation that accounts for the
entire discrepancy, we do find that the subset of ``free-form'' lens
models are more accurate and provide more realistic uncertainties than
``parametric models'' for this sight-line.} A larger sample of 10-100
lensed \SNeIa\ could provide a robust evaluation of systematic biases
in lens models.  Until such a sample exists, it is advisable
to \change{increase the estimated uncertainty of predicted
magnifications to match the dispersion observed across multiple lens
models.}
\end{abstract}

@@

\changeG{
Galaxy clusters can be used as cosmic telescopes to magnify distant
background objects through gravitational lensing, which can
substantially increase the reach of deep imaging surveys.  The lensing
magnification enables the study of objects that would otherwise be
unobservable because they are either intrinsically
faint \citep[e.g.][]{Schenker:2012,Alavi:2014} or extremely
distant \citep[e.g.][]{Franx:1997,Ellis:2001,Hu:2002,Kneib:2004,Richard:2006,Richard:2008,Bouwens:2009a,Maizy:2010,Zheng:2012,Coe:2013,Bouwens:2014,Zitrin:2014}.
Background galaxies are also {\it spatially} magnified, allowing for
studies of the internal structure of galaxies in the early universe
with resolutions of $\sim$100
pc \citep[e.g.]{Stark:2008,Jones:2010,Yuan:2011,Livermore:2015}.
}

\changeG{
Gravitational lensing can also provide a powerful window onto the {\it
transient} sky through an appropriately cadenced imaging survey.  The
flux magnification from strong-lensing clusters is especially valuable
for the study of $z>1.5$ supernovae
(SNe) \citep[e.g.]{Kovner:1988,Kolatt:1998,Sullivan:2000,Saini:2000,Gunnarsson:2003,Goobar:2009,Postman:2012},
which are still extremely difficult to characterize in unlensed
fields \citep[e.g.]{Riess:2001,Riess:2007,Suzuki:2012,Rodney:2012,Rubin:2013,Jones:2013}.
}

\changeG{
In the case of lensed SNe, we can also reverse the experimental setup:
instead of using strong-lensing clusters to study distant SNe, we can
use the SNe as tools for examining the lenses \citep{Riehm:2011}.  The
most valuable transients for testing and improving cluster lens models
would be {\it strongly lensed} SNe that are resolved into multiple
images \citep{Holz:2001,Oguri:2003}.  Transients that are lensed into
multiple images can also become cosmological tools, as the measurement
of time delays between the images can provide cosmographic information
to constrain the Hubble parameter \citep{Refsdal:1964} and other
cosmological parameters \citep{Linder:2011}.  We have recently
observed the first example of a multiply-imaged
SN \citep{Kelly:2015}, and expect to detect the reappearance of this
object (called ``SN Refsdal'') within 5 years, delivering a precise
test of lens model predictions \citep{Oguri:2015,Sharon:2015}.
Although detections of such objects are currently very
unlikely \citep{Li:2012}, they will become much more common in the
next decade \citep{Coe:2009,Dobke:2009}, and may be developed into an
important new cosmological tool.
}

\changeG{
In addition to time delays from multiply-imaged SNe, we can also
put cluster mass models to the test with the much more common category
of lensed Type Ia SNe.  
\citet[][hereafter P14]{Patel:2014} and \citet{Nordin:2014} presented
independent analyses of three lensed SNe, of which at least 2 are
securely classified as Type Ia SNe -- all found in the Cluster Lensing
and Supernova survey with Hubble (CLASH, PI:Postman, HST Program ID
12068, \citealt{Postman:2012}).  Both groups demonstrated that these
standard candles can be used to provide accurate and precise
measurements of the true absolute magnification along a random sight
line through the cluster.  Although in these cases the SNe were used
to {\it test} the cluster mass models, one could in principle
incorporate the measured magnifications of Type Ia SNe into the
cluster as additional model constraints.  In that role, Type Ia SNe
have the particular value that they can be found anywhere in the
cluster field.  Thus, they can deliver model constraints in regions of
``middle distance'' from the cluster core, where both strong- and
weak-lensing constraints are unavailable.
}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{FIG/snTomas_magnifications}
\caption{ 
Comparison of the observed lensing magnification to predictions from
lens models. Solid vertical lines show the constraints from SN \tomas\
derived in Section~\ref{sec:Magnification} using the SALT2 (red) and
MLCS2k2 (blue) fitters, with shaded regions marking the total
uncertainty for each. Markers with horizontal error bars show the
median magnification and 68\%\ confidence region from each of the 14
lensing models.  Circles indicate models that use only strong-lensing
constraints, while diamonds denote those that also incorporate
weak-lensing measurements.  Models shown with open markers were
constructed using only data available before the start of the Frontier
Fields observations.  Filled markers indicate models that use
additional input constraints, including new multiply imaged systems
and redshifts.  The eight models shown in black at the top are from
the ``parametric'' family, and the six in green at the bottom are
``free-form.''  Dashed lines mark the unweighted mean of each model
family and shaded regions show the standard error of the mean.
\label{fig:lensingtest} }
\end{center}
\end{figure}

@@

In Figure~\ref{fig:lensingtest} the model predictions are plotted
alongside the observed magnification of SN \tomas, derived in
Section~\ref{sec:Magnification}.  This comparison shows that these 14
models are largely consistent with each other. Naively treating each
model as an independent prediction for the magnification (and ignoring
their quoted uncertainties), one would get a mean for the full sample
of $\mu=2.51\pm0.34$.  This is separated from the observed SN
magnification by $\delta\mu/\mu=27\%$, which is only a 1.2$\sigma$
difference.

The models shown in Figure~\ref{fig:lensingtest} are separated along
the $y$ direction into two broad classes, with 
eight \change{so-called} {\it parametric}\footnote{\change{Although this
nomenclature is becoming standard in the literature, it is somewhat
misleading, as the pixels or grid cells in free-form models are
effectively parameters as well. Perhaps ``simply-parameterized'' would
be more accurate, though we adopt the more common usage here.}}
models on top and six {\it free-form} models on the bottom.
Broadly speaking, the parametric models use parameterized density
distributions to describe the arrangement of mass within the cluster,
typically associating massive dark matter halos with the positions of
bright cluster member galaxies. Therefore, parametric models rely (to
varying degrees) on the assumption that the observed light from
cluster galaxies is a good tracer of the cluster's dark matter.
Free-form models divide the cluster into a grid, generally using a
\change{multi-scale grid} to get better sampling in denser regions. Each grid cell
is assigned a mass or a potential, and then the mass values are
iteratively refined to match the observed lensing
constraints. \change{In some cases an adaptive grid is used so
that the grid spacing itself can also be modified as the model is
iterated \citep[e.g.][]{Liesenborgs:2006,Merten:2009}.}

@@

Figure~\ref{fig:lensingtest} also separates the models based on the
scope of input data constraints used.  Ten of the models rely only
on strong-lensing constraints (plotted as circles), while the other
four also use weak-lensing measurements (diamonds).  Ten of the
models were constructed using only pre-HFF data (open symbols), and
four others added new multiply-imaged systems and redshifts.

@@

At the outset of the HFF survey, only 33 multiply-imaged galaxies
behind Abell 2744 were known.  One might expect that the addition of
new lensing constraints from the HFF data would improve the model
constraints and reduce the tension between the predicted and observed
magnification.  However, for \changeG{two} of the most recent
models \citep{Jauzac:2014c,Lam:2014} that include new strong-lensing
constraints, the predicted magnification is still significantly higher
than the observed value.  Again the CATS model family provides a
useful case study.  The Jauzac model shares the same lens modeling
software (LensTool), and the same primary methodology as the earlier
CATS models.  A key difference is that the Jauzac model incorporates
many new multiply imaged galaxies and corrects a mis-identified
multiply-imaged system near the SN \tomas\ position.  These
improvements should in principle make the Jauzac model magnification
estimates more accurate, though we in fact see the opposite result:
the Jauzac model predicts a $\mu$ that is higher than the measured
value by \changeG{$4.3\sigma$.}

This shift to higher magnifications is not, however, unique to the
SN \tomas\ position.  \citet{Jauzac:2014c} noted that their updated
mass model of Abell 2744 results in a systematic increase in the
magnification values across the cluster field. Examining a sample of
$\sim$30 multiple images, \citeauthor{Jauzac:2014c} found that the
magnifications increased by a factor of $\sim1.5$ relative to pre-HFF
models.  Although this single sight-line can only provide a very
limited test of the model, the \changeG{$4.3\sigma$} discrepancy is at
least a strong suggestion that improving the number and quality of
strong-lensing constraints can still lead to magnification maps that
are susceptible to systematic biases.

\change{
\subsection{Misidentification of System 3}
\label{sec:MisidentificationOfSystem3}
}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{FIG/system3.png}
\caption{ 
The disputed component of the multiply-imaged galaxy System 3. The
original position, as given in \citet{Merten:2011} is marked with a
dashed magenta circle labeled 3.3. The solid magenta circle shows the
revised location as proposed in \citet{Jauzac:2014c}.  Both positions
are $\sim$10\arcsec\ from the SN location.  The inset panel shows the
other two components of this multiply-imaged system, 3.1 and 3.2 (on
the same scale as the main panel), which are located north-east of the
cluster center.
\label{fig:system3} }
\end{center}
\end{figure}

\change{
It is important to note that in regards to the impact on this
particular sight-line, not all strong-lensing constraints are equal.
An error in the association of multiple images or in the redshift of a
multiply-imaged galaxy would have a more significant impact if that
system has a projected position close to our SN
sight-line \changeG{\citep[see][for a quantitative assessment of this
effect]{Johnson:2014}.}  It happens that there is one such system, for
which the position of a multiple image near SN \tomas\ is presently
disputed.  }

\change{
This multiply-imaged galaxy was originally labeled as {\it System 3}
in \citet{Merten:2011}.  As shown in Figure~\ref{fig:system3}, it is
stretched into two adjacent arcs northeast of the cluster core (images
3.1 and 3.2), with a third image on the western edge of the
strong-lensing region (image 3.3 at 00:14:18.595,
-30:23:58.42).  \citet{Richard:2014} echoed this initial
identification in producing the {\tt CATS} models, which we cite in
Table~\ref{tab:PredictedMagnifications} and
Figure~\ref{fig:lensingtest}.  In developing the {\tt Sharon-v2}
models, \citet{Johnson:2014} provided a secure spectroscopic
constraint of $z=3.98\pm0.02$ for this system, based on a spectrum of
the combined 3.1+3.2 source. The identification of the original image
3.3 has been called into question by two independent analyses.  Using
HFF imaging data, \citet{Lam:2014} suggested an alternative third
image for this system roughly 8\arcsec\ to the south, which we will
call \33p\ (00:14:18.39, -30:24:06.53).
However, \citeauthor{Lam:2014} rejected this possibility based on a
difference in colors between \33p\ and images 3.1 and 3.2.  In
contrast, \citeauthor{Jauzac:2014c} argue that the position \33p\
is correct, and find that reassigning this multiple image results in a
tighter model reconstruction for the locations of other
multiply-imaged systems in the vicinity.
}

@@

\change{
Is it possible that \tomas\ is an example of a peculiar stellar
explosion that does not follow the relationship between light curve
shape and luminosity observed in normal Type Ia SNe?  In
Sections~\ref{sec:SNID} and \ref{sec:PhotometricClassification} we
classified SN Tomas as a normal Type Ia SN based on both the
spectroscopic and photometric evidence.  This rules out the
possibility that \tomas\ belongs to a different class of normal SN
explosions (Type Ib, Ic, or II). In
Section \ref{sec:LightCurveFitting} we fit the \tomas\ light curve to
determine a luminosity distance and found that the light curve shape
and color are consistent with a Type Ia SN of average light curve
width, with minimal dust extinction.  This excludes the possibility
that \tomas\ is one of the sub-class of faint and fast-declining Type
Ia SNe like SN 1991bg.  }

@@

\changeG{
At least for this particular sight-line, the free-form models perform
better both in the sense that the mean and standard error for this
subset ($2.34\pm0.27$) is closer to the measured value ($2.00\pm0.28$)
than is the parametric set ($2.59 +- 0.36$).  These free-form models
also deliver more realistic uncertainties (with the exception of the
Bradac(v2) model -- see \citet{Wang:2015} for further discussion of
the changes made from v1 to v2 of that model).  This may indicate that
the free-form approach in general is more successful in capturing the
uncertainty from biases inherent to the mass modeling exercise, such
as the mass sheet degeneracy and more complex ``approximate
invariances'' \citep{Liesenborgs:2012,Schneider:2014}.  It may also be
the case that the greater flexibility of the free-form models makes
them better suited for predicting magnifications of sources that fall
outside the strong-lensing region -- such as SN \tomas.  }

@@

\change{
A promising avenue for exploring the origins of systematic biases in
cluster lens models is through the use of simulated data.  One can
start with very deep high-resolution multi-band imaging on an unlensed
field that has a fairly complete spectroscopic redshift catalog, such
as the Hubble Ultra Deep Field.  Then a simulated galaxy cluster is
placed in the field, and the background galaxies are distorted into
arcs and multiple images using a well-defined lensing prescription.
The artificially lensed images can then be distributed to lens
modeling teams who attempt to reconstruct the (known) mass profile of
the simulated cluster.  This exercise has recently been pursued with a
set of synthetic clusters similar to those observed in the HFF program
(Meneghetti et al. in prep).  Preliminary analysis of this simulation
comparison suggests that \changeG{magnifications tend to be
overestimated} for sources that lie outside the strong-lensing region
along the minor axis direction of an elongated cluster.  Our analysis
of SN \tomas\ here indicates that such simulation efforts will be an
important step for moving toward precision science with cluster-lensed
sources.  }
